Reparametrization of COM-Poisson Regression Models with Applications in the Analysis of Experimental Data

### 2017-10-31 article.Rnw
Modify preamble according to SMJ class

\documentclass[a4paper]{article}

\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{bm}
\DeclareRobustCommand{\rchi}{{\mathpalette\irchi\relax}}
\newcommand{\irchi}[2]{\raisebox{\depth}{$#1\chi$}}

\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue,
  urlcolor=blue}

\usepackage[bottom]{footmisc}
\usepackage{geometry}
\geometry{lmargin=3cm, rmargin=3cm, tmargin=3cm, bmargin=3cm}

% Algorithm
\usepackage[english, vlined, ruled]{algorithm2e}
\SetAlCapSty{}
% \SetAlCapFnt{\footnotesize}
% \SetAlCapNameFnt{\footnotesize}

\usepackage{natbib}
% \bibliographystyle{humannat}
\bibliographystyle{agsm}

\usepackage{lipsum}
\usepackage{float}
\usepackage{mathpazo}

@@

%-----------------------------------------------------------------------
\title{Reparametrization of COM-Poisson Regression Models with
  Applications in the Analysis of Experimental Data}

\author{
  Eduardo E. R. Junior\thanks{Corresponding author:
    \href{mailto:jreduardo@usp.br}{\nolinkurl{jreduardo@usp.br}}}
    \hspace*{.8mm}\thanks{Department of Exact Sciences, ESALQ-USP,
    Piracicaba, S\~{a}o Paulo, Brazil} \and
  Walmes M. Zeviani\thanks{Department of Statistics, UFPR, Curitiba,
    Paran\'{a}, Brazil} \and
  Wagner H. Bonat\footnotemark[3] \and
  Clarice G. B. Dem\'{e}trio\footnotemark[2]
}

\date{\today}

@@

\begin{abstract}

  In the analysis of count data seldom the equidispersion assumption is
  suitable, hence the Poisson regression model is inappropriate in many
  situations. The COM-Poisson is a member of the exponential family, has
  the Poisson and geometric distributions as special cases and the
  Bernoulli distribution as a limiting case. It can deal with both under
  and overdispersed count data. Therefore it is a suitable distribution
  to the analysis of dispersed count data. In spite of the nice
  properties of COM-Poisson, the location parameter of the distribution
  does not represent the conditional mean making difficult
  interpretation in a regression structure. In this paper we present a
  very simple reparametrization based on mean approximation. The
  estimation and inference is based on likelihood and simulation study
  showed that the maximum likelihood estimators are unbiased and
  consistent for both regression and precision parameters. Furthermore,
  we observed empirical correlation between regression and precision
  parameters close to zero suggesting the orthogonality feature in the
  proposed mean reparametrized model. We present applications of the
  proposed model through three case studies with over, under and
  equidispersed counts. Results show improvements over the conventional
  approaches. Therefore, its use in the analysis of count data is
  encouraged. The computational routines for fitting of original and
  reparametrized COM-Poisson models are available in the supplementary
  material.

\vspace{0.1cm}
\noindent\textbf{keywords:} COM-Poisson, Over/Under-dispersion, Count
data, Likelihood inference.
\end{abstract}

\pagebreak

>>>>

%-------------------------------------------
% Document class
\documentclass[submit]{smj}

%-------------------------------------------
% Personal packages and definitions
\usepackage{amsfonts}
\usepackage{bm}
\DeclareRobustCommand{\rchi}{{\mathpalette\irchi\relax}}
\newcommand{\irchi}[2]{\raisebox{\depth}{$#1\chi$}}

% Algorithm
\usepackage[english, vlined, ruled]{algorithm2e}
\SetAlCapSty{}

\usepackage{float}

@@

% -------------------------------------------
% Authors and affiliations
\Author{Eduardo E. Ribeiro Jr\Affil{1},
  Walmes M. Zeviani\Affil{2},
  Wagner H. Bonat\Affil{2},
  Clarice G. B. Dem\'{e}trio\Affil{1}
  and John Hinde\Affil{3}
}
\AuthorRunning{Ribeiro Jr \textrm{et al.}}

\Affiliations{
\item Department of Exact Sciences,
  University of S\~{a}o Paulo - ESALQ,
  Piracicaba,
  SP, Brazil
\item Department of Statistics,
  Paran\'{a} Federal University,
  Curitiba,
  PR, Brazil
\item School of Mathematics, Statistics and Applied Mathematics,
  National University of Ireland,
  Galway,
  Galway, Ireland
}

%-------------------------------------------
% Corresponding author
\CorrAddress{Eduardo E. Ribeiro Jr,
             Department of Exact Sciences,
             Luiz de Queiroz College of Agriculture - ESALQ,
             University of S\~{a}o Paulo - USP,
             Piracicaba, S\~{a}o Paulo,
             P\'{a}dua Dias, 11, Avenue, CEP--13.418-900
             Brazil}
\CorrEmail{jreduardo@usp.br}
\CorrPhone{(+55)\;41\;9\;8711\;9034}
\CorrFax{(+55)\;19\;3447\;6021}

%-------------------------------------------
% Title and shor title
\Title{Reparametrization of COM-Poisson Regression Models with
  Applications in the Analysis of Experimental Data}
\TitleRunning{Reparametrization of COM-Poisson Regression Models}

%-------------------------------------------
% Abstract
\Abstract{
  In the analysis of count data seldom the equidispersion assumption is
  suitable, hence the Poisson regression model is inappropriate in many
  situations. The COM-Poisson is a member of the exponential family, has
  the Poisson and geometric distributions as special cases and the
  Bernoulli distribution as a limiting case. It can deal with both under
  and overdispersed count data. Therefore it is a suitable distribution
  to the analysis of dispersed count data. In spite of the nice
  properties of COM-Poisson, the location parameter of the distribution
  does not represent the conditional mean making difficult
  interpretation in a regression structure. In this paper we present a
  very simple reparametrization based on mean approximation. The
  estimation and inference is based on likelihood and simulation study
  showed that the maximum likelihood estimators are unbiased and
  consistent for both regression and precision parameters. Furthermore,
  we observed empirical correlation between regression and precision
  parameters close to zero suggesting the orthogonality feature in the
  proposed mean reparametrized model. We present applications of the
  proposed model through three case studies with over, under and
  equidispersed counts. Results show improvements over the conventional
  approaches. Therefore, its use in the analysis of count data is
  encouraged. The computational routines for fitting of original and
  reparametrized COM-Poisson models are available in the supplementary
  material.
}

%-------------------------------------------
% Key-words
\Keywords{
COM-Poisson; Count data; Over/Under-dispersion; Likelihood inference
}

@@
